%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{}

% make footer span full page width
\setlength{\footskip}{18pt}
\fancyhfoffset[L]{0in}
\fancyhfoffset[R]{0in}

% footer text
\fancyfoot[L]{\scriptsize Updated in March 2026}
\fancyfoot[C]{\scriptsize Arnesh Banerjee $\cdot$ CURRICULUM VITAE}
\fancyfoot[R]{\scriptsize \thepage}

% remove lines
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Arnesh Banerjee} \\ \vspace{3pt}
    \small
    \faPhone\ +91-8902037524 \ $|$\
    \faEnvelope\ \href{mailto:arnesh.banerjee.ds27@heritageit.edu.in}{arnesh.banerjee.ds27@heritageit.edu.in} \ $|$\
    \faGlobe\ \href{https://arneshbanerjee.github.io/}{website} \ $|$\
    \faLinkedin\ \href{https://www.linkedin.com/in/arnesh24/}{arnesh24} \ $|$\
    \faGithub\ \href{https://github.com/ArneshBanerjee}{ArneshBanerjee}
\end{center}

    
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Heritage Institute of Technology, Kolkata}{GPA: 8.876}
      {Bachelor of Technology in Data Science}{Aug. 2023 -- June. 2027}
  \resumeSubHeadingListEnd


%-----------RESEARCH INTERESTS-----------
\section{Research Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Multi-Agent Systems $\cdot$ Reinforcement Learning $\cdot$ AI Governance $\cdot$ Applied Machine Learning $\cdot$ AI Safety \& Alignment $\cdot$ Large Language Models $\cdot$ Reinforcement Learning from Human Feedback $\cdot$ Medical Imaging
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Jadavpur University}{November 2025 -- Present}
      {Advisor: Prof. Debotosh Bhattacharjee}{Remote}
      \resumeItemListStart
        \resumeItem{Achieved 98.10\% Dice and 96.39\% IoU on breast thermography tumor segmentation using a ResNet34 + ASPP + ViT decoder with SE attention, evaluated via 5-fold cross-validation.}
        \resumeItem{Conducted a rigorous ablation study (20 training runs) across U-Net, ResNet-only, and hybrid architectures, demonstrating that simpler models can match complex designs and highlighting generalization trade-offs in medical imaging.}
        \resumeItem{Built a fully automated cross-validation pipeline with checkpointing, experiment logging, and reproducible training, producing publication-ready comparative metrics for medical image analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {New Jersey Institute of Technology}{June 2025 -- July 2025, August 2025 - November 2025}
      {Advisor: Prof. Arnob Ghosh}{On Site, Virtual}
      \resumeItemListStart
        \resumeItem{Constructed a cost-model training dataset for a modified Safe RLHF pipeline leading to improved results in the cost-model.}
        \resumeItem{Designed and tested comparative 800 datapoint safety benchmark against state-of-the-art LLMs (GPT, DeepSeek, Gemini, Qwen, Mistral).}
        \resumeItem{Demonstrated 50\% higher safety compliance than ChatGPT 5 across benchmark scenarios.}
    \resumeItemListEnd

    \resumeSubheading
      {Heritage Institute of Technology}{October 2024 -- March 2025}
      {Advisor: Prof. Arpita Talukdar}{On Site}
      \resumeItemListStart
        \resumeItem{Developed a dual-stage ML framework for breast cancer diagnosis and recurrence prediction using WDBC and WPBC datasets, evaluating RF, SVM, Logistic Regression, MLP, and XGBoost with stratified 10-fold cross-validation.}
        \resumeItem{Implemented RFE and SFS feature selection with SMOTE and GridSearchCV tuning, improving WPBC accuracy to 93.67\% (SVM + RFE) and WDBC to 97.77\% (LogReg + RFE).}
        \resumeItem{Conducted comparative performance analysis and interpreted clinically relevant nuclear features, reporting stable cross-validated results with confidence intervals.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\resumeItemListStart
    \resumeItem{Kartik Pandit, Sourav Ganguly, \textbf{Arnesh Banerjee}, Shaahin Angizi, Arnob Ghosh. 2025. Certifiable Safe RLHF: Fixed-Penalty Constraint Optimization for Safer Language Models. arXiv preprint arXiv:2510.03520.}
    \resumeItem{Ayushi Bhattacharjee, \textbf{Arnesh Banerjee}, Arpita Talukdar. 2026. Recursive and Wrapper-Based Feature Selection for Breast Cancer Diagnosis and Prognosis. In the proceedings of the 4th Analytics Global Conference (AGC 2026), March 2026. \textbf{Oral.}}
\resumeItemListEnd

%-----------ONGOING RESEARCH-----------
\section{Ongoing Research}
\resumeItemListStart
    \resumeItem{\textbf{Arnesh Banerjee}, Debotosh Bhattacharjee. Multiscale Transformer-Enhanced U-Net with Level-Set Regularization for Breast Thermography Segmentation. \textit{Manuscript in preparation.}}
    \resumeItem{Kartik Pandit, Sourav Ganguly, Arnesh Banerjee, Avirup Chakraborty, Arnob Ghosh. Analyzing Historical Revisionism in LLMs in the Context of Indian History. \textit{Advisor: Prof. Arnob Ghosh.}}
    \resumeItem{\textbf{Arnesh Banerjee}, Ayushi Bhattacharjee, Anubrata Monday. Curriculum Augmented RLVR for Reasoning in Small Language Models. \textit{Advisor: Jhalak Dutta.}}
    \resumeItem{\textbf{Arnesh Banerjee}, Ayushi Bhattacharjee. Understanding the Limitations of LLMs in Mathematical Reasoning. \textit{Advisor: Prof. Subhajit Dutta.}}
\resumeItemListEnd


%-----------PROJECTS-----------
\section{Important Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Co-evolutionary RL for Autonomous Drone Warfare Simulation - AI Governance and Accountability} $|$ \emph{Python, PyTorch, Stable-Baselines3, Gymnasium}}{2026}
\resumeItemListStart
\resumeItem{Built a co-evolutionary multi-agent simulation using reinforcement learning (PPO) and behavior trees to model strategic interactions in asymmetric conflict, investigating whether adaptive defensive agents can keep pace with autonomous offensive capabilities.}
\resumeItem{Implemented a self-play training framework with Elo rating tracking to study escalation dynamics between competing agent populations, connecting iterative best-response learning to game-theoretic equilibrium concepts.}
\resumeItem{Implemented drone navigation, detection, and engagement via RL policy accounting for constraints such as limited battery, uneven terrain, weather, and other environmental factors.}
\resumeItem{Engineered a curriculum learning pipeline with domain randomization and cost asymmetry analysis (\$20K drone vs. human-equivalent costs) to quantify how economic incentive structures drive algorithmic decision-making in adversarial settings.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Candidate Smart Profile Competency Score Calculator} $|$ \emph{Python, Scikit-Learn} $|$
\href{https://github.com/ArneshBanerjee/Smart-Competency-Diagnostic-and-Candidate-Profile-Score-Calculator}{GitHub Link}}{SIH 2024}
\resumeItemListStart
\resumeItem{Built an ML system to predict job categories from resumes using Random Forest, leading to SIH 2024 Round 2.}
\resumeItem{Recommended personalized courses and job roles based on extracted skills and competency scoring.}
\resumeItemListEnd

\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, C, Java, SQL} \\
     \textbf{Machine Learning}{: PyTorch, Scikit-Learn, Keras, H2O, CatBoost, XGBoost} \\
     \textbf{Data \& Visualization}{: pandas, NumPy, Matplotlib, Seaborn, Plotly} \\
     \textbf{Frameworks \& Tools}{: Flask, FastAPI, Shiny, Docker, Git} \\
     \textbf{Relevant Courses}{: Operating Systems, Database Management System, Data Structures, Algorithms, Machine Learning, Data Mining, Data Warehousing} \\
     \textbf{Research Tools}{: Jupyter Notebook, LaTeX}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
